Using simulation to optimize the sampling design of fisheries-independent trawl surveys

### 2018-11-18 analysis/paper/sim_survey_paper.Rmd
Improve the plot_survey function (include true, caught and measured length and age distributions)

pa <- plot_surface(a, mat = "N", scene = "scene1", showscale = FALSE) %>% 
  add_annotations(x = 0.05, y = 0.9, xref = "paper", yref = "paper", showarrow = FALSE,
                  text = "a)")
pb <- plot_surface(b, mat = "N", scene = "scene2", showscale = FALSE) %>% 
  add_annotations(x = 0.05, y = 0.9, xref = "paper", yref = "paper", showarrow = FALSE,
                  text = "b)")

export_plot(p, file = "analysis/paper/figures/plot_surface.png", width = 800, height = 370)
knitr::include_graphics("figures/plot_surface.png")
```

```{r, echo = TRUE, eval = FALSE}
a <- make_grid(n_div = 1, shelf_depth = 200,
               shelf_width = 100, depth_range = c(0, 1000))
b <- make_grid(n_div = 4, shelf_depth = 500, 
               shelf_width = 0, depth_range = c(0, 1000))
plot_grid(a)
plot_grid(b)
```

a <- make_grid() %>% 
  plot_grid(showscale = TRUE) %>% 
  add_annotations(x = 0, y = 1, xref = "paper", yref = "paper", showarrow = FALSE,
                  text = "a)")
b <- make_grid(n_div = 4, shelf_depth = 500, shelf_width = 0, depth_range = c(0, 1000)) %>% 
  plot_grid(showscale = FALSE) %>% 
  add_annotations(x = 0.01, y = 1, xref = "paper", yref = "paper", showarrow = FALSE,
                  text = "b)")
p <- subplot(a, b)

The `sim_distribution` function distributes the population simulated using `sim_abundance` throughout the grid generated using `make_grid`. Table \@ref(tab:par) outlines the default settings used for the function and the case study. In addition to supplying objects produced by `sim_abundance` and `make_grid`, this function requires two closures that describe the age-year-space covariance and the relationship with depth. Here we use `sim_ays_covar` and `sim_parabola` to control these relationships and a wide range of age and year specific distributions can be obtained by tweaking a few parameters in these closures. Below we run a default `sim_distribution` call, which generates a population that forms tight clusters that are more strongly correlated across years than ages, and another call that generates a population that is more diffuse (i.e. wider range) and exhibits stronger correlation across ages than years. Distributions can also be forced to be the same across ages and years by using the `group_ages` and `group_years`, respectively, arguments in the `sim_ays_covar` closure. In other words, these parameters can be modified to control the degree of age-specific clustering and inter-annual site-fedelity exhibited by the simulated population. Note that the resolution of the default grid is high and, as such, the simulations below may take minutes to complete. Also note that the key functions in the SimSurvey package have been set-up to be pipe [`%>%`; @bache2014] friendly.

```{r, echo = TRUE, eval = FALSE}
plot_distribution(a, ages = 1:3, years = 1:3, type = "heatmap")
plot_distribution(b, ages = 1:3, years = 1:3, type = "heatmap")
```

The function `sim_survey` can be used to simulate data from one survey over a population simulated using `sim_distribution`:

```{r, echo = TRUE, eval = FALSE}
s <- sim_survey(d, n_sims = 1,
                q = sim_logistic(k = 2, x0 = 3),
                trawl_dim = c(1.5, 0.02),
                set_den = 2 / 1000,
                lengths_cap = 500,
                length_group = 1,
                ages_cap = 10)
```

Again, this function retains all the objects listed in `d` and adds objects that detail the set locations (`setdet`) and sampling details (`samp`).

@@

>>>>

@@

pa <- plot_surface(a, mat = "N", scene = "scene1", showscale = FALSE) %>% 
  add_labels(x = 0.05, y = 0.9, text = "a)")
pb <- plot_surface(b, mat = "N", scene = "scene2", showscale = FALSE) %>% 
  add_labels(x = 0.05, y = 0.9, text = "b)")

export_plot(p, file = "analysis/paper/figures/plot_surface.png", width = 800, height = 370)
knitr::include_graphics("figures/plot_surface.png")

```{r, echo = TRUE, eval = FALSE}

a <- make_grid(n_div = 1, shelf_depth = 200,
               shelf_width = 100, depth_range = c(0, 1000))
b <- make_grid(n_div = 4, shelf_depth = 500, 
               shelf_width = 0, depth_range = c(0, 1000))
plot_grid(a)
plot_grid(b)

a <- make_grid() %>% 
  plot_grid(showscale = TRUE) %>% 
  add_labels(x = 0, y = 1, text = "a)")
b <- make_grid(n_div = 4, shelf_depth = 500, shelf_width = 0, depth_range = c(0, 1000)) %>% 
  plot_grid(showscale = FALSE) %>% 
  add_labels(x = 0.01, y = 1, text = "b)")
p <- subplot(a, b)

The `sim_distribution` function distributes the population simulated using `sim_abundance` throughout the grid generated using `make_grid`. Table \@ref(tab:par) outlines the default settings used for the function and the case study. In addition to supplying objects produced by `sim_abundance` and `make_grid`, this function requires two closures that describe the age-year-space covariance and the relationship with depth. Here we use `sim_ays_covar` and `sim_parabola` to control these relationships and a wide range of age and year specific distributions can be obtained by tweaking a few parameters in these closures. Below we run a default `sim_distribution` call, which generates a population that forms tight clusters that are more strongly correlated across years than ages, and another call that generates a population that is more diffuse (i.e. wider range) and exhibits stronger correlation across ages than years. Distributions can also be forced to be the same across ages and years by using the `group_ages` and `group_years`, respectively, arguments in the `sim_ays_covar` closure. In other words, these parameters can be modified to control the degree of age-specific clustering and inter-annual site-fidelity exhibited by the simulated population. Note that the resolution of the default grid is high and, as such, the simulations below may take minutes to complete. Also note that the key functions in the SimSurvey package have been set-up to be pipe [`%>%`; @bache2014] friendly.

```{r, echo = TRUE, eval = FALSE}

plot_distribution(a, ages = 1:3, years = 1:3, type = "heatmap")
plot_distribution(b, ages = 1:3, years = 1:3, type = "heatmap")

The function `sim_survey` can be used to simulate data from one survey over a population simulated using `sim_distribution`. This function simulates the sampling process of the survey and, as such, requires a closure for defining catchability as a function of age and definitions of the design of the survey. Specifically, the `q` argument requires a closure, such as `sim_logistic`, for defining the probability of catching specific age groups, trawl dimensions are defined in the `trawl_dim` argument, and set, length and age sampling effort are defined using the `set_den`, `lengths_cap` and `ages_cap` arguments, respectively. Multiple simulations of the same survey can be run using the `n_sims` argument, however, it is important not to request large numbers of simulations because this function can quickly deplete a computers RAM. Defaults used in the function and for the case study roughly correspond to the assumed catchability in NAFO division 3Ps as well as the sampling protocol used in the survey of this stock (Table \@ref(tab:par)). Below we use `sim_survey` to simulate two surveys over the same population, of which one is set-up to have higher sampling effort than the other.

set.seed(438)
pop <- sim_abundance() %>% 
  sim_distribution()
a <- pop %>% 
  sim_survey(n_sims = 5,
             set_den = 1 / 1000,
             lengths_cap = 100,
             ages_cap = 5)
b <- pop %>% 
  sim_survey(n_sims = 5,
             set_den = 5 / 1000,
             lengths_cap = 500,
             ages_cap = 25)

Again, this function retains all the objects listed in the output of `sim_distribution` and adds data.tables that detail the set locations (`setdet`) and sampling details (`samp`). Catchability corrected abundance matrices, named `I` and `I_at_length`, are also produced and added to the output; these matrices are useful for comparing the true abundance available to the survey to abundance estimates obtained using survey-based or model-based analyses of the simulated survey data. Specific surveys can be explored using the `plot_survey` function, which uses plotly [@sievert2018] and crosstalk [@cheng2016] in the background to link the bubble plot of aggregate set catch to the histogram of lengths and ages sampled to facilitate explorations of set-specific catches. The plots generated below have been combined here into a static plot for this paper (Figure \@ref(fig:survey)).

```{r, echo = TRUE, eval = FALSE}

plot_survey(a, which_sim = 1, which_year = 20)
plot_survey(b, which_sim = 1, which_year = 20)

```{r survey, fig.cap = "- Bubble plots and histograms of set catches produced by `plot_survey` when supplied survey data simulated using `sim_survey` under relatively a) high and b) low sampling effort. Note that the first simulation of the survey in the first year is depicted here."}

plot_a <- plot_survey(a, which_sim = 1, which_year = 1)
plot_b <- plot_survey(b, which_sim = 1, which_year = 1)

p <- subplot(plot_a, plot_b, nrows = 2) %>% 
  add_labels(text = "a)", x = 0, y = 1, yshift = 20, xshift = -20) %>% 
  add_labels(text = "b)", x = 0, y = 0.5, yshift = 20, xshift = -20)

export_plot(p, file = "analysis/paper/figures/plot_survey.png", width = 500, height = 600)
knitr::include_graphics("figures/plot_survey.png")

- You need to fix up the aspect ratios and margins in the plot_survey subplot
- Mention the `n_sims` argument, mention RAM limitations, and then move to `sim_survey_parallel`
